\RequirePackage{plautopatch}
\documentclass[uplatex,
paper=a4,
fontsize=18pt,
jafontsize=16pt,
number_of_lines=30,
line_length=30zh,
baselineskip=25pt,
]{jlreq}
\usepackage[utf8]{inputenc}
\usepackage{pxfonts}
\usepackage[T1]{fontenc}
\author{yokoP}
\title{eigo}
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\scriptsize\space\today\space\normalsize\textgt{よこぷり☆}P\thepage}
\begin{document}

\lhead{\scriptsize 主語ー英文練習}
1.  You leave school.

2.  I take Tom to the town.

3.  You run.

4.  She gives a note to Mary.

5.  They say thanks to you.

6.  We come to the town.

7.  He eats an apple.

8.  She gets a note.

9.  They see a cake.

10.  You go to the town.

11.  We draw a picture.

12.  You leave school.

13.  I buy a pencil.

14.  She meets Tom.

15.  He takes a cake from Mary.

16.  They take Mary to the library.

17.  You read a book.

18.  We tell him a message.

19.  You have a note.

20.  I sit on a chair.


\newpage
\lhead{\scriptsize 動詞ー現在・過去 活用練習}
1.  行く:   現在形: go   過去形: went

2.  描く:   現在形: draw   過去形: drew

3.  読む:   現在形: read   過去形: read

4.  伝える:   現在形: tell   過去形: told

5.  もらう:   現在形: take   過去形: took

6.  会う:   現在形: meet   過去形: met

7.  座る:   現在形: sit   過去形: sat

8.  去る:   現在形: leave   過去形: left

9.  買う:   現在形: buy   過去形: bought

10.  走る:   現在形: run   過去形: ran

11.  手に入れる:   現在形: get   過去形: got

12.  来る:   現在形: come   過去形: came

13.  買う:   現在形: buy   過去形: bought

14.  つれていく:   現在形: take   過去形: took

15.  描く:   現在形: draw   過去形: drew

16.  読む:   現在形: read   過去形: read

17.  来る:   現在形: come   過去形: came

18.  あげる:   現在形: give   過去形: gave

19.  手に入れる:   現在形: get   過去形: got

20.  持っている:   現在形: have   過去形: had

21.  食べる:   現在形: eat   過去形: ate

22.  座る:   現在形: sit   過去形: sat

23.  行く:   現在形: go   過去形: went

24.  会う:   現在形: meet   過去形: met

25.  去る:   現在形: leave   過去形: left

26.  もらう:   現在形: take   過去形: took

27.  言う:   現在形: say   過去形: said

28.  走る:   現在形: run   過去形: ran

29.  伝える:   現在形: tell   過去形: told

30.  見る:   現在形: see   過去形: saw


\newpage
\lhead{\scriptsize 動詞現在形ー英文練習}
1.  You take an apple from Mary.

2.  I give a pencil to Mary.

3.  He gives a note to Kenta.

4.  They take Mary to school.

5.  She sits on a chair.

6.  We say hello to him.

7.  You tell her a message.

8.  I come to the town.

9.  You meet Kenta.

10.  We leave the town.

11.  She buys a pencil.

12.  They read a book.

13.  He takes a note from Tom.

14.  They see a note.

15.  He gets a chair.

16.  She goes to school.

17.  We run.

18.  You have a cake.

19.  I eat a cake.

20.  You draw a picture.


\newpage
\lhead{\scriptsize 動詞過去形ー英文練習}
1.  He met Kenta.

2.  She gave a cake to Tom.

3.  I met Tom.

4.  They took Mary to school.

5.  You took a cake from Tom.

6.  You drew a picture.

7.  I saw a pencil.

8.  We gave a chair to Tom.

9.  He told him a message.

10.  You came to the library.

11.  You left the town.

12.  They bought an apple.

13.  She said hello to you.

14.  I ran.

15.  They read a book.

16.  You ate a cake.

17.  We went to the library.

18.  You had a cake.

19.  He sat on a chair.

20.  She got a pencil.


\newpage
\lhead{\scriptsize 主語ー\scriptsize 動詞現在形ー\scriptsize 動詞過去形ー英文練習}
1.  You came to the town.

2.  I run.

3.  She got an apple.

4.  They say hello to her.

5.  You took a cake from Kenta.

6.  We go to the town.

7.  They sit on a chair.

8.  You buy a chair.

9.  I ran.

10.  He met Mary.

11.  We came to the library.

12.  She takes Kenta to school.

13.  You see a cake.

14.  You had a chair.

15.  He gives an apple to Kenta.

16.  She told him a message.

17.  We ate a cake.

18.  I draw a picture.

19.  They left the town.

20.  You read a book.

\end{document}